---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# infunx

<!-- badges: start -->
<!-- badges: end -->

This is a collection of R utilities functions for me, but maybe also for you.

Functions may be added, specifications of functions may change or become obsolete, and names may change without notice.

This is a collection of codes that cannot be included in `{infun}` due to licensing reasons.

## Installation

You can install the development version of `{infunx}` like so:

``` r
install.packages("remotes")
remotes::install_github("indenkun/infunx")
```

## Example

load library.

```{r example}
library(infunx)
```

### `t_test_stats()`

Performs one and two sample t-tests from descriptive statistics.
In short, it is like `python`'s `scipy.stats.ttest_ind_from_stats`.

This is partially based on the code of `t.test()` in `{stats}` on R 4.2.2 by R Core Team.

```{r}
# The mean value of a is 2, with a standard deviation of 1 and a sample size of 3.
# The mean value of b is 0, with a standard deviation of 1 and a sample size of 3.
a <- c(1, 2, 3)
b <- c(-1, 0, 1)
# Using t.test() of stats for this 2-group t-test, we get the following.
stats::t.test(a, b)
```

This t-test can be performed on aggregated descriptive statistics data with `t_test_stats()`.

```{r}
t_test_stats(mean_x = 2, std_x = 1, n_x = 3,
             mean_y = 0, std_y = 1, n_y = 3)
```

One sample t-tests can also be performed.

```{r}
stats::t.test(a)
t_test_stats(mean_x = 2, std_x = 1, n_x = 3)
```

## License

* GPL-2.0 license

## Imports packages

* `{stats}`

## Notice

* The email address listed in the DESCRIPTION is a dummy. If you have any questions, please post them on ISSUE.
